%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:aa
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete,
% awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
 
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Phuong Van}{Nguyen}
\address{The University of Kiel, R.104, Leibnizstraße 3, 24118, Kiel, Germany}
\mobile{(+49) 1764-380-7215} 
%%% Social
\email{phuong.nguyen@economics.uni-kiel.de}
\homepage{https://www.quantitative-economics.uni-kiel.de/en/doctoral-candidates}
%\github{posquit0}
%\linkedin{posquit0}
%%% Optionals
\position{PhD Candidate{\enskip\cdotp\enskip}Quantitative Economics}
%\quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  { The Kellogg School of Management }
  {2211 Campus Dr \\
  Evanston, IL 60208, USA\\
\\
}
\letterdate{\today}
\lettertitle{The position as an Empirical Research Fellow (Job ID: 35096)}
\letteropening{Dear Sir/Madam}
\letterclosing{Sincerely,}
%\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today }
  {Phuong Van Nguyen~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader
%%% Make a title for Cover Letter using letter data
\makelettertitle
%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}

I am a fourth-year PhD candidate at the University Of Kiel, Germany. My primary research interests are business cycle modeling, monetary economics, Bayesian estimation of DSGE models and applied Bayesian and Frequentist Macroeconometrics. I am happy to find your vacancy on the Northwestern Univerisity's site which perfectly matches my qualification and experience.

\cvparagraph{Current career?}


Firstly, my professional qualification has been considerably acquired by studying around the world. In particular, I obtained a Bachelor degree in Vietnam and a Master with distinction in Japan. Currently, I am pursuing a PhD in Germany. In addition, I pursued an international-reputed Advanced Study Program (ASP) at the Kiel Institute for the World Economy (IfW), where all courses were taught by world-renowned professors from leading universities around the globe \footnote{https://www.ifw-kiel.de/institute/education/advanced-studies-program/}. I also enrolled in a wide range of summer schools in economics and econometrics in France, Italy and Spain.

I have 6-years of relevant experience conducting research in monetary economic.  For example, since 2013 I have been a junior research fellow at the Banking Academy, a research and teaching institute of central bank of Vietnam. Currently, on the other hand, I am doing three PhD projects which focus on the application of the DSGE model to macroeconomic policy analysis and forecasting. The first paper answers the question that which model (closed- or open economy DSGE settings) should the central bank use to forecast? The empirical evidences in favor of closed-economy DSGE framework are shown. This paper was, then, successfully accepted for presentation at the 21th Dynamic Econometrics Conference at the George Washington University in USA.  The second paper examines the Vietnamese business cycle in an estimated DSGE model. The finding indicates that supply-side shock is a dominant source. Currently, I am conducting the third project that will examine the business cycle of the 5-biggest ASEAN economies (Singapore, Malaysia, Thailand, Indonesia and Philippines). The empirical finding from an estimated DSGE model with the financial friction will show how the local and global Recessions such as the 1997 Asian and the 2008 financial crises impact the aggregate activities in these countries. 


Last but not least, I have relevant experience of teaching at both undergraduate and graduate levels in various fields of international finance, international trade and investment, mathematical methods for economics, statistic, econometric in Vietnam, Japan and Germany. Additionally, my long-term experience of using the statistical software packages (Matab, R, Stata, Eviews and Python) enables me to conduct empirical researches effectively. For instance, my master thesis was successfully accepted for publication on the Australian Economic Review. More specifically, I examine the long-run relationship between the unemployment rate and the labour force participation rate in Australia. Using cointegration analysis, I find that there is no long-run relationship between these two variables in Australia. This finding supports the unemployment invariance hypothesis. I also have actively participated in various conferences around the world (Germany, Italy, Albania, and USA) as a presenter.
My Academic goal



\cvparagraph{Academic goal}

My great goal is to become a high-ranked economist in the ASEAN region. It has strongly motivated me to gain specialized knowledge in advanced countries (Japan, European nations). On the other hand, I really want to gain valuable experience of research at leading institutes and universities in the world. Working as an empirical Research Fellow at the Kellogg School of Management, will be definitely an excellent opportunity for me to turn my great goal into action. 

With a strong background in quantitative economics, statistics and computer programming, I would be confident to fulfill your requirements.

I am looking forward to your positive reply.


\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}